%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------
\name{Cesar Arguello} % Your name
\address{cesar.n.arguello.martinez.gr@dartmouth.edu \\ www.carguellom.com}
\begin{document}
\title{cesar_vita}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Ph.D. in Computer Science}{September 2022 - Present}{Dartmouth College}{Hanover, NH, USA}
  \vspace{-.1cm}
  \textbf{Advisor}: Dr. David Kotz\\ \textbf{Research Area}: Security and Privacy in the Lifecycle of IoT for Consumer
Environments
  \vspace{-.65cm}
  \item[]
\end{rSubsection}

\begin{rSubsection}{B.S. in Physics \& Computer Science}{August 2018 - May 2022}{University of Florida}{Gainesville, FL, USA}
  \vspace{-.65cm}
  \item[]
\end{rSubsection}

\begin{rSubsection}{International Baccalaureate Diploma Programme (IB)}{August 2016 - May 2018}{UWC Red Cross Nordic}{Flekke, Norway}
  \vspace{-.65cm}
  \item[]
\end{rSubsection}
\end{rSection}

%--------------------------------------------------------------------------------------- 
%   INDUSTRY EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Insustry Experience}
\begin{rSubsection}{Product Development Engineer Intern}{January 2022 - May 2022}{Intel Corporation}{Santa Clara, CA, USA}
  \item Designed, developed, and debugged sort test programs for server products. 
  \item Tested, validated, modified, and redesigned circuits to guarantee component margin to
specification. 
  \item Analyzed and evaluated component specification versus performance to ensure optimal
match of component requirements with production equipment capability.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Research EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
  \begin{rSubsection_ra}{Gradute Research Assistant}{January 2023 - Present}{Dartmouth College}{Hanover, NH, USA}{Department of Computer Science}{Dr. David Kotz and Dr. Timothy Pierson}
    \item Maintain a C, C++, and Python codebase for a harmonic radar controller, ensuring optimal performance and reliability for various research applications. 
    \item Design and implement experiments and circuit prototypes for novel applications of harmonic radars in IoT security, focusing on advancing research and practical use cases.
    \item Develop comprehensive research plans targeting conference and journal publications while actively reviewing and discussing relevant literature on IoT security.
  \end{rSubsection_ra}
  \begin{rSubsection_ra}{Research Assistant}{June 2021 - May 2022}{Univeristy of Florida}{Gainesville, FL, USA}{Florida Institute of Cybersecurity}{Dr. Sara Rampazzi and Dr. Kevin Butler}
  \item Designed and developed experiments to test theoretical frameworks on EM side channel disassembly.
  \item Collected, processed, and analyzed EM traces using statistical and machine learning models.
  \item Developed research plans leading to the successful completion of project deliverables (publications, presentations, etc.).
  \end{rSubsection_ra}
  \begin{rSubsection_ra}{Research Assistant}{May 2021 - May 2022}{Univeristy of Florida}{Gainesville, FL, USA}{Department of Physics, SuperCDMS HVeV-DMC Data Analysis and Simulations Team}{Dr. Tarek Saab}
  \item Designed and developed Ionization Measurement with Phonons At Cryogenic Temperatures (IMPACT) simulation files for the Geant4 simulator.
  \item Analyzed Geant4 simulation results with Python.
  \item Lead discussions about Geant4 simulation results. 
  \end{rSubsection_ra}

  \begin{rSubsection_ra}{Research Assistant}{August 2020 - February 2021}{Univeristy of Florida}{Gainesville, FL, USA}{Department of Mechanical and Aerospace Engineering, ADAMUS Lab}{Dr. Riccardo Bevilacqua}
    \item Designed, developed, and deployed C++ libraries for control of a CubeSat's magnetometers, EPS, and battery, utilizing I2C protocol communication and integrating with Beagle Bone Black microcontroller.
    \item Tested and debugged flight component prototypes.
    \item Authored weekly project reports highlighting software development achievements, challenges faced, and innovative solutions implemented during the development of flight software.
  \end{rSubsection_ra}
\end{rSection}

%----------------------------------------------------------------------------------------
%   TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching Experience}
\begin{rSubsection_ta}{Gradute Teaching Assitant}{September 2022 - January 2023}{Dartmouth College}{Hanover, NH, USA}{CS50: Software Design and Implementation}
  \item Developed and maintained automated grading scripts using Bash and Python to evaluate student assignments.
  \item Conducted in-depth code reviews for programming projects, providing constructive feedback to enhance code quality, efficiency, and adherence to best practices.
  \item Held office hours to provide one-on-one mentorship to students on course material and programming projects.
\end{rSubsection_ta}
\begin{rSubsection_ta}{Undergraduate Teaching Assistant}{January 2021 - May 2021}{Univeristy of Florida}{Gainesville, FL, USA}{CDA3101: Introduction to Computer Organization}
\item Assisted student achieved proposed academic goals by leading discussions on lecture material. 
\item Supported instructors by managing the evaluation of course assignments and providing detailed feedback to students.
\item Held office hours to review course material, answer general questions, and provide some assistance on assignments.
\end{rSubsection_ta}
\end{rSection}


%---------------------------------------------------------------------------------------
% PUBLICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
  \begin{rSubsection_Conference}{Conference Papers}
    \item Ravindra Mangar, \textbf{Cesar Arguello}, David Inyangson, Tina Pavlovich, Karen Gareis, and Tushar Jois. \textit{Proceedings of the 56th ACM Technical Symposium on Computer Science Edu-
cation V. 1 (SIGCSE TS)}, 2025. Acceptance rate 33\%.
    \item \textbf{Cesar Arguello}, Beatrice Perez, Timothy J. Pierson, and David Kotz. Detecting Battery Cells with Harmonic Radar. \textit{Proceedings of the ACM Conference on Security and Privacy in Wireless and Mobile Networks (WiSec)}, 2024. Acceptance rate 21\%.
    \item Beatrice Perez, \textbf{Cesar Arguello}, Timothy J. Pierson, Gregory Mazzaro, and David Kotz. \textit{Proceedings of the IEEE Military Communications Conference (MILCOM)}, 2023. Acceptance rate 40\%. 
  \end{rSubsection_Conference}

  \begin{rSubsection_Journal}{Journal Articles}
  \item Timothy J. Pierson, \textbf{Cesar Arguello}, Beatrice Perez, Wondimu Zegeye, Kevin Kornegay, Carl Gunter, and David Kotz. We need a “building inspector for IoT” when smart homes are sold. \textit{IEEE Security \& Privacy}, 2024. 
  \end{rSubsection_Journal}

  \begin{rSubsection_Poster}{Posters}
  \item \textbf{Cesar Arguello}, Hunter Searle, Sara Rampazzi, Kevin Butler. [Poster]: A practical methodology for ML-Based EM Side Channel Disassemblers. \textit{Proceedings of the 2022 Poster Session of the 7th IEEE European Symposium on Security and Privacy}, 2022.
  \end{rSubsection_Poster}
\end{rSection}


%---------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
\begin{rSubsection_project}{SDR FM Radio Demodulator}{August 2024}
Real Time FM radio demodulator for HackRF and RTL SDR written in Python. \underline{Future Work}: Support other SDRs and improve audio streaming. [\href{https://github.com/carguelloM/sdr-fm-radio}{GitHub Repository}]
\end{rSubsection_project}

\begin{rSubsection_project}{Bi-detectional Intercom}{Novermber 2021}
Bi-directional intercom based on operational amplifiers, BJT transistors, and diodes. [LTSPice Sim]
\end{rSubsection_project}

\begin{rSubsection_project}{Shell for UNIX-Based Systems}{January 2021}
A shell for Unix-based system with basic capabilities, such as
I/O redirection, piping, wildcarding, tilde-expansion, and background processing. [\href{https://github.com/carguelloM/CPshell}{GitHub Repository}]
\end{rSubsection_project}


\end{rSection}

%---------------------------------------------------------------------------------------
% Other Academic Activities 
%----------------------------------------------------------------------------------------
\begin{rSection}{Other Academic Activities}
\textbf{Student Participant}, CyberTruck Challenge \hfill \textit{June 2024}
\end{rSection}
%--------------------------------------------------------------------------------------- 
%   OTHER EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Experience}
\begin{rSubsection}{Audio Visual Specialist}{May 2019 - March 2022}{J. Wayne Reitz Union}{Gainesville, FL, USA}
  \item Managed and installed audio-visual equipment for shows, meeting, and events held at the
J. Wayne Reitz Union.
  \item Aided costumers with audio-visual technical difficulties.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & English, Spanish \\
Programming Languages & Python, MATLAB, C++, C, LaTex, x86\\
Frameworks & Pytorch \\
Software & Microsoft Suite, Git, GDB, Wireshark \\
Web skills & HTML5, CSS \\
\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
%   Awards
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards}
\textbf{Latin Honors}, Cum Laude B.S. \hfill \textit{May 2022} \\
\textbf{Honor Society}, Phi Betta Kappa \hfill \textit{May 2022} \\
\textbf{Academic Scholarship}, Davis UWC Scholar \hfill \textit{August 2018} 
\end{rSection}

\end{document}
